A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
Edited up to 4.1.1

\begin{abstract}
We performed an online survey to examine risk perceptions surrounding wearable computing devices. We controlled for different data types that might be captured, who might have access to that data, and whether it was captured on a wearable device or a smartphone (i.e., to control for familiarity with the technology). We surveyed 1,785 participants about 72 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks. Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies. The results of this study can be used to guide future research in wearable device security, especially research that helps to protect sensitive data and guides the design of effective privacy notifications and indicators.
\end{abstract}

@@

To this end, we surveyed 1,785 Internet users to determine their risk perceptions surrounding the operation of wearable devices. In this work, we contribute the following: \\[-0.8cm]

@@

\subsubsection{Comprehension Questions}
Because participants might be biased to specific devices or companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable device. Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which would be the basis for all questions on wearable computing risks. We highlighted the capabilities of this device and described several use cases. To ensure that participants had read and understood this device's capabilities, we presented them with two comprehension questions.

\subsubsection{Wearables Scenarios}
We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first. All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}. We created an initial pool of 292 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were:

@@

To parallel Fischhoff \etal's risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved. We randomized whether they performed the ranking for risks or benefits first. The prompt is listed in Appendix \ref{sec:prompt}. The question format was as follows:

@@

\subsection{Recruitment and Analysis Method}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old, living in the United States, and having a successful HIT completion rate of 95\% or above. Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants. We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, leaving us with a total sample size of 1,785. Of these, 57.87\% were male, with a median age of 29 ($\sigma$ = 10.37).

@@

%SE: Edited up to here.
%Comment on independence of observations, differences between public/work, and end the subsection

{\color{red} Serge, this paragraph can be re-worded as you see fit. I just plopped in some stuff.} this test violates that assumption of CHI square, however, based on the condition randomization and very large sample size, we do not believe this to be an issue. Nonetheless, we checked this by also performing the analysis by using only one data point per recipient (to preserve that assumption), and yielded the same results. There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.

Participants had different sensitivities depending on if they perceived that their data would be shared with an application or a person. We found the top and bottom ten concerns with respect to a non-human audience (app's servers) versus a human audience (friends, work contacts, and public). Participants were more uncomfortable about privacy and theft (i.e. frequency of sex, photos at home, and passcodes to doors). when sharing data with an application. They were also more uncomfortable sharing phone or text conversations and credentials (i.e. username and password for websites, credit card information) to a human audience than to a server. Additionally, they concerned more concerned On the other hand, participants were comfortable sharing behavioral patterns and personal opinions (i.e. phone use, opinions of people, eye patterns, and food eaten) with an app's server rather than a human audience. For a human audience, participants were most comfortable sharing data which would come up in conversation (i.e music on their device, if one was having fun, and if one if busy or interruptible), but found these topics more disturbing to share with an app's server.   {\color{red} should we creatively include stats for these in the appendix, in a space-conscious way?}.

>>>>

\begin{abstract}
We performed an online survey to examine risk perceptions surrounding wearable computing devices. We controlled for different data types that might be captured, who might have access to that data, and whether it was captured on a wearable device or a smartphone (i.e., to control for familiarity with the technology). We surveyed 1,784 participants about 72 data types, 4 data recipients, and 2 devices to quantify risk perceptions across a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these risks. Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies. The results of this study can be used to guide future research in wearable device security, especially research that helps to protect sensitive data and guides the design of effective privacy notifications and indicators.
\end{abstract}

@@

To this end, we surveyed 1,784 Internet users to determine their risk perceptions surrounding the operation of wearable devices. In this work, we contribute the following: \\[-0.8cm]

@@

\subsubsection{Comprehension Questions}
Because participants might be biased to specific devices or companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable device. Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which would be the basis for all questions on wearable computing risks. We highlighted the capabilities of this device and described several use cases. To ensure that participants had read and understood this device's capabilities, we presented them with two multiple-choice comprehension questions.

\subsubsection{Wearables Scenarios}
We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first. All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}. We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were:

@@

To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved. We randomized whether they performed the ranking for risks or benefits first. The prompt is listed in Appendix \ref{sec:prompt}. The question format was as follows:

@@

\subsection{Recruitment and Analysis Method}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18 years old, living in the United States, and having a successful HIT completion rate of 95\% or above. Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants. We filtered out an additional 100 participants (4\% of 2,250) due to incomplete responses, leaving us with a total sample size of 1,784. Of these, 57.87\% were male, with a median age of 29 ($\sigma$ = 10.37).

@@

%Comment on independence of observations, differences between public/work, and end the subsection

We note that this chi-square test violates the assumption of independence of observations, since each participant responded to multiple scenarios. However, based on the randomization of treatments and very large sample size, we do not believe that this impacted our results. Nonetheless, we repeated the analysis using only one randomly-selected data point per participant and observed that our previous results held: participants were significantly more concerned about having their data seen by actual humans (as opposed to app servers), though the specific human had no observable effect (i.e., between the public, friends, and work contacts).

%SE: this needs to be rewritten below.

We compared the top and bottom ten concerns between a non-human audience (app's servers) and a human audience (friends, work contacts, and the public). While many of the most and least concerning scenarios were the same between these two groups, participants were more uncomfortable about privacy and theft (i.e. frequency of sex, photos at home, and passcodes to doors) when sharing data with an application. They were also more uncomfortable sharing phone or text conversations and credentials (i.e. username and password for websites, credit card information) to a human audience than to a server. Additionally, they concerned more concerned On the other hand, participants were comfortable sharing behavioral patterns and personal opinions (i.e. phone use, opinions of people, eye patterns, and food eaten) with an app's server rather than a human audience. For a human audience, participants were most comfortable sharing data which would come up in conversation (i.e music on their device, if one was having fun, and if one if busy or interruptible), but found these topics more disturbing to share with an app's server.

There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.
